\label{chapt:uncategorized}

\section{Aesthetics advice and other conversations}

\subsection{Rlaan Aesthetics}
Conversation (excerpts) on Rlaan aesthetics

A: we'll start with the "how much is alive" part not too much,
although there are a lot of organics used, especially internally.
parts of the life support system are made from arguably living
material, and the automated repair systems rely upon living organisms

Q: hmmm.. is it something that can be seen?

A: excepting one case - not really, no. Not unless, sometime far down
the line we do interiors. The only visible exception is the effect
that having living secretion sites would have on what we might want
damage maps to look like. for visual range, the Rlaan are heavily blue
shifted relative to our visual spectrum

Q: near uv?

A: yes, they can see in near UV, but their red-end range is inferior
to ours, and their peak response point is also shifted up in
frequency, although their frequency responses are more even than
ours. They use 5 pigments vs. our 3.

Q: interesting.. very much so. the reason I had previously brought up
the visual range, was for colours.. so one could get an idea of what
they would look like or rather one of the reasons

A: their color choices may look a bit dark (we don't percieve blue
tones as intensely) and some of them bland in contrast (different
pigment response curves)

Q: ok.. so no seeing through the hulls and that whatnot.. what was the
next one?

A: (although there'll be images on the hull we can't see at all, and
some of the red-end of our hulls will just look black to them - their
sun isn't a yellow star like ours - no superman for them ;-))

Q: *nods* I thought that maybe some insignias and markings might look
broken or even fairly faded, as parts of it, may go out of our visual
range which would give it an interesting look

A: indeed.  the 5 models we have for the Rlaan are pretty good
indicators of style for their military craft no visible engines (the
Rlaan just do gravitics) Big dual purpose radiator/shield manipulator
fins

Q: how about for the larger craft.. battleships, and bases?

A: so, we've got 3 Rlaan small craft, and 2 Rlaan capital vessels
 right now a destroyer and a cruiser

Q: so.. do you want the stationary rlaan craft to follow the same
general gist? squatish insect puapa (sp)

A: no, they should have a lot more radial symmetry rather than
bilateral in 4s preferably so, for the stations My first thought is to
go for a cored, squashed, pruned, and resurfaced sea urchin look :-)
less vaguely: an ovoid (as opposed to a spheroid, hence squashed) with
an empty center at its rotational axis (cored) with intermittent long,
thin spires and smaller fins (pruned)

Q: more towards crystalline, or with the metallic chiton/membrane
look?

A: the latter, as with the underside spires on the (destroyer?) with a
surface similar to the topology and aesthetics of the cap-ships,
excepting that civilian installations have a {\em much} more
whitewashed color scheme (resurfaced)

Q: ok.. sounds a lot more simplified then I think had been coming out
of some folks looking to do rlaan

A: well, that's first approximation the surface isn't smooth though,
and each of the four sections isn't perfectly ovoid so there's plenty
of detailing to be done

Q: *nods* irregularities and so forth

A: but everything is rounded use the 2 capships as your guide to
surfacing

Q: ok.. I'd been coping the uv maps for a little bit of a guide on
some of the ships

A: Just as long as it doesn't get mistaken for Mon Calimari design,
you're probably somewhere on the right track :-)

Q: heh

A: so, the key is this 1.design a very interesting quarter of a
station, for any Rlaan station, really, then make 3 more of them.  The
only exception for this would be at the very small end (too
specialized for arbitrary symmetry) or on something like a shipyard
where it's not a practical design for enclosing things

Q: *nods* hmm.. so you can have fairly expansive and maybe even
elongaded forms.. that still follow the general outlines of this.. or
are elongated forms out?

A: in what sense elongated?

Q: well.. I wrote that thinking long.. but if you're going with
general crab like shapes.. then elongated would actually be from the
center out , rather than along the length of the core say the core is
the y access.. you could have the center along the y and z axis fairly
wide out, but not along the y axis in comparison to the z and x

A: so radially symmetric around y axis hence z=x but span(y)!=span(z)
well, yes they're radially symmetric, not spherical but the bases
won't look like them they just borrow the radial concept here are some
important things to remember about the Rlaan

Q: *nods* radial and rounded.. I'm trying to get the feel for the
general way in which forms are done

A: Consider their music as indicitave in some sense of their attitude
towards construction: they like to take lots of simple themes and
plaster, superimpose, and alternate among them The result, to human
ears, is often hopelessly noisy, or monotonously simple, or both two:
The Rlaan are, to quote the "Tough guide to the known galaxy" "Really
Alien" they aren't aliens with forehead ridges

Q: *nods* truly different

A: They are foreign to us, and as such are not beings that should lend
themselves to comfort in our perception of their being and their
edifice thus, in creating things for them there is a line to walk
between creating questions of "but why would they do that?" and "No
rational being could have done anything remotely like that"

Q:hmm.. sounds a lot like a form of brainstorming that is drawing
based..

A: So, having a large, prominent object of non-discernable purpose
that something is built around, or a placement policy for certain
necessary things that seems... odd is good, but having recognizeable
objects in clearly wrong places just makes them look like idiots or
lunatics e.g. placing all of the bathrooms for human visitors inside
trees - strange, possibly alien misconception. Placing all of the
bathrooms outside the hull.... um.... yeah

Q: you're looking for something that has the taste of something that
was done naturally, not something that was randomly placed together

A: The best approach is to pick some fairly arbitrary goals but ones
that can be consistently applied the key to the particular mindset of
the Rlaan is that these should likely be fairly simple, but there
should be many of them and they should interact

Q: oh.. *nods* had to think about that a moment when I say natural.. I
mean that it flows as one piece. and not like it was a pirate stealing
from various races to build something

A: The huldra and Lodur, I think do a better job of making one wonder
what the designer was thinking than do the smaller craft

Q: *nods* the smaller craft look little like different pieces slapped
onto a craft to make it look different

A: they also look more familiar - they're more identifiable

Q: there was something I did want to ask you about.. about technology
in vs..

A: sure

Q: is it ok to base technology off those portions of vs that use the
magic theme.. so your antigrav and stuff like that

A: Some of them are based off of that, yes

Q: I know that you are doing that with rlaan.. or it would seem
so.. but in general I get the idea that folks should shy away from
technology that relies on the magic theme based off of existing.. that
is

A: gravitics-spacetime warping is pretty heavily in the VS scheme of
things right now -- there's always a danger when playing around with
*magic* that you'll paint yourself into a corner

Q: so.. should greebles for rlaan look more like veins and spines?
aside from things jutting out..  also, should the fins you get with
ships, be present to any degree on stationary craft

A: mmm. some spines, not too many veins. More blisters, and opened
blisters with internal protrusions, and overlayed regions of different
construction.  The fins should still be there T the Rlaan like to have
lots of radiator surface

Q: ok

A: and, as mentioned, there's lots of shield control circuitry
embedded in them

\subsection{Textual ship descriptions}

Some very, very brief descriptions of vessels

Manufacturer: Mechanist Defense Contracting, under contract from Confederation Navy

Class: Battle Cruiser\\
Designation: Battle Cruiser Mk. 32\\

the armament on the Mechanist battlecruiser is fairly simple\\
48 heavy beams, and a bunch of PD turrets\\
and designed such that all 48 beams can face dead ahead\\
12 can face dead stern\\
and 12- 16 can face to each side\\
so, a limited, if potent, vessel\\
a tapered appearance, starting at a somewhat ovoid part, and narrowing as it goes towards the front - then stopping suddenly in what amounts to a wide, narrow mouth with 3 4x1 restricted movement LR beam turrets as jutting tusks\\
on the top, behind the mouth and up the slope somewhat, a less restricted 4x1 turret. Up the slope more and to each side, more 4x1 turrets\\
the bottom and top are symmetric\\
around the rim of the ovoid part\\
12 cocoon shaped turrets jut out, positioned such that the gun can be pointed forwards and backwards\\
slanting down on both sides to angle in if need be\\
but heavily restricted in the other degree of motion\\
to the rear of the turrets, a brief ring at 45 degree angle slope with PD turrets\\
then a sudden extreme slope that curves around and gives rise to a bumpy engine and whatnot rear\\
4 docking bays, each located in a cutaway area in the side\\


Manufacturer: Andolian Military and Andolian Protectorate Fleet, for crewing by Andolian and Klk'k Forces.\\
Class: Destroyer\\
Designation: Nietzsche\\

Visual description:\\

The basic shape of the main hull is roughly cylindrical. The thickness
of the body does not vary overmuch, though it does vary, except at the
front and rear. At the rear, it tapers abruptly for a very short time,
then curves in on itself, creating a caldera, or bowl-like depression
into the rear of the vessel.  The main engine exhausts are in this
inset area.  On the tapered part of the ring around the engine bowl
are four point-defense turrets, one top, bottom, and to each
side. Coming out from the main hull are four projections, one pair on
top and bottom, not too much after the engine area, and one pair on
the sides, forward of the top and bottom pair, but overlapping
somewhat in that they begin before the other pair ends. These
projections are quite thick, and shaped something like a compromise
between a circle and an equilateral triangle.  Imagining them as
triangles one would say that they were aligned such that the top and
bottom pair pointed forwards, and the two side projections pointed
rearwards.  The projections extend out about the radius of the main
body, whereupon they are capped by a thick, slightly wider plate, much
as one would imagine a toadstool, shitake, or portabello would appear
if the stalk were almost as thick as the head, and the head flat on
the top and rounded on the bottom and edge.  Just below the cap,
embedded in the projections, are large engine thrusters. The engine
thrusters in the top/bottom pair are larger than those in the side
pair.  On top of the cap, at each of the "corners" is a largish
turret, though not a massive one, somewhat tilted down from the flat
plane of the top of the cap such that its gun can depress below
level. Each such turret contains a single gun.  Forward of the side
projections somewhat, the cylindrical main body differentiates.  The
top portion becomes a bundle of six tubes (for launching anti-capital
missiles) around a larger central projection, two above, two below,
and one to each side in slightly svertically squashed hexagonal
fashion.  The tubes are not actually touching each other, and the area
in between them is filled in solid as is the area between the tubes
and the central projection. Beneath this bundle of tubes is a
hangar/docking bay. The combination of the docking bay and the
collection of tubes are slightly slimmer than the main body of the
ship. The tubes extend slightly beyond the end of the hangar.  The
central tube area terminates in an inset sensor array and two small
turrets, one to each side.  The missile launcher tubes terminate as
one would expect them to, flush with the base of the turrets on the
central projection. There is a tractor beam turret on both sides of
the hangar, and a disabling turret on the bottom lip of the hangar.

There are various PD and anti-fighter turrets, but their position
isn't as important at this level of description, save to say that I
see 3 anti-fighter turrets on the sides of each projection to
discourage loitering beneath the guns, and that PD coverage must be
excellent :)

To describe a bit more...

The open face of the docking bay is in the forward direction, and
though, from the outside, it is clearly much deeper, the initial open
area is somewhat shallow as it terminates in a large armored door that
protects the inner docking bay.

Looking at the Nietzsche from dead ahead of the vessel, one might
imagine the missile launcher tubes as the hideously deformed
descendants of magazine from a six-shooter revolver. Relative to the
crisp radial symmetry of the six-shooter, the tubes are stretched
further apart horizontally, maintaining vertical and horizontal
symmetry, but not radial. Likewise, the aperatures where the missiles
exit are vastly smaller by comparison to the size of the tubes
themselves than in a revolver. Most notably of course, these tubes do
not at all revolve, nor move at all. So they really do not look all
that much like a revolver magazine; perhaps the image of a revolver is
only the quick shadow of a thought that comes from knowing that one is
staring at six tubes, each of which holds death, and each of which has
opened its dark mouth in your direction....


Materials/texture/greebles/etc. appearance: A purely military vessel,
there are no vulnerable areas exposed unnecessarily.  However, there
are various sensor arrays, shield emitters, escape pod launchers, and
maneuvering thrusters located on the hull, so it is not just a giant
smooth armored mass. That being said, it IS a military vessel, and the
dominant feature of its hull will still be the nearly seamless
overlapping plates of multiple layers of armor.

Approximate Sizes: length of main body - 1500 meters, including
engines, hangar bay and launch tubes.  radius of main body, 150
meters.  length of projection caps ~ 450 meters

Hopefully this gives you something to work with without completely
smothering your creative license :)

Anaxander:\\ 

(Design work previously ascribed to the Anaxander will be shuffled
onto one of the other Aeran ships - as that thread has been silent for
a year, I think it's probably not a big deal - and I think I like what
I'm coming up with better)

Description 1: (a quick verbal sketch of a quick freehand sketch -
I'll write more later)

A tube with length:diameter ~ 6:1 very slightly squashed in the
vertical dimension. Narrowed vertically somewhat at front to attach to
hammerhead-style frontal region. Hammerhead has teardrop shaped cross
section viewed from the side. Point of teardrop faces backwards. At
the rear of the ship there are two similar projections on the sides of
the 'engine'. There is no narrowing, rather the projections expand
rapidly to merge into hull. Height of front teardrop ~1/2 diameter
length (base to point) ~1 diameter (more or less) and rear teardrops
are somewhat larger. Width of hammerhead - artist's discretion + field
of fire for mounted PD + anti-small craft turrets. At bottom rear of
vessel, forward slightly of exhaust region is an underslung docking
bay, with an opening at the rear, facing back and slightly downwards.

There are six major projections extending radially from the ship,
three rear, and three front. The three rear are in a top, bottom-left,
bottom-right radial symmetry, and the front three are shifted 60
degrees to a bottom, top-right, top-left radial symmetry. The rear
projections begin just after the engine region and are narrow at the
back, wider at the front, have a gradual slope on the rear side, a
flat top, and a very steep returning slope (something vaguely like a
rose thorn that has been pruned of the pointy part). They do not
return all the way to their original height level relative to the hull
and instead merge into spinal gun emplacements that sit on top of the
hull, each gun emplacement housing three long, large weapons.
Attached to the flat top of each projection is a triple-mouthed
torpedo turret. The three fore projections are longer, less stout, and
have maneuvering engines through their middles. They are faced
oppositely (flatter region back-facing, pointy region forward-facing)
and are topped with gun turrets.

Additional gun emplacements are present on top of the engine section
and on the bottom of the docking bay. The longer projections are (in
height) ~30\% of the ship's length, the shorter rear ones ~20\%. On
the exterior facing flattened sides of the hammerheads (both front and
rear) are "sensor stuff". Overall ship's length estimate for scaling
perspective ~ 2.1km.

Ultra-brief ship's history:\\ 

The Anaxander is old, and even with retrofits is aging
significantly. It was the main Aeran cruiser at the beginning of the
Rlaan-Aera conflict, having already been produced in some number. As
newer designs (some already in the pipeline) were phased in, the
Anaxander moved to less prestigious roles. While still a vessel of
noteworthy offensive potential, it now almost universally finds itself
attached to task forces rather than leading them.



Purist Star Car (Name to be decided later):\\
LIHW Star Bus (Name to be decided later):\\

First, some context:\\

Ownership of personal spacecraft is most akin to ownership of such
boats as one would have to dock at the local marina today. Thus, while
not of unreachable expense (only the luxury yachts are luxury yachts,
even in space) private craft are not ubiquitous and mass transit, both
public and private, is much relied upon.

The bulk of civilian passenger transport vessels (that is, excluding
mercantile transport) would fill one of the following niches (with
modern analogue in parentheses):

Interplanetary Personal Transit ("Car")\\
Interplanetary Charter and Rental ("Limo/Rental/Taxi/Charter Bus/Charter plane")\\
Interplanetary Mass transit ("Bus/Light-rail")\\
Interstellar Mass transit ("Commercial airliner")\\
Interstellar Recreational ("Cruise ship")\\
Interstellar Jump Ferry (no direct analog - taking one's car/small boat across an ocean isn't common enough)\\
Interstellar Personal Transit("Yacht/Private Plane - not necessarily of luxury variety")\\


\subsection{The Aesthetics of Deucalion with tangents on the Klk'k}
A conversation on appearances

T: so, first off, a general comment (not directly about the drawing) about Deucalion's ancestry - namely, he has designer genes that apper to draw from several groups as opposed to being a standard Shaper variant of anything, so inferences directly from or to the Shapers are fuzzy.\\
A: how old do you picture him?\\
T: early thirties\\
say 32 for a round number\\
haven't entirely nailed that down yet, but about that -\\
A: cool, not enough to be 'old' but old enough to have a past\\
T: but this is also in the context of a longer expected life-span, gene-smithing, etc\\
A: so he looks 20-something?\\
T: the detrimental effects of aging won't have kicked in yet\\
A: roger\\
T: it's less that he looks 20-something or that he is particularly youthful than just the above \\
A: ah, gotcha--should look young yet mature\\
at once\\
am I right?\\
T: something like that ;-)\\
an extended "prime of life" if you will\\
rather than the very brief peaking of our modern phsyiology\\
if, in 1200 years we can't age much more gracefully, it's time to shoot the geneticists\\
A: all right. what else? given any thoughts to the scar suggestion?\\
T: he heals quite well, so it'd be more apt to due some subtle discolorations rather than overt scars\\
we'll see how it turns out\\
if it looks good, we'll work with it, if not, we can re-examine it\\
also might work better to limit the scarring on the face, as faces are delicate in their perception to begin with\\
A: I suggested decoloring--to ditch the overused stitch-mark clich\\
a line of lighter skin, just enough to be noticeable, probably\\
T: arms and such are much easier to get away with if the face appears over marred\\
but yeah, give it a try, and we'll see how it looks\\
A: ok.\\
T: speaking of markings\\
he'll need a high bandwidth I/O port\\
A: what does that look like?\\
T: discrete, not overt, near flush with the skin (self covering when not active), but obviously not of organic origin. Small region towards the classic back of the head/base of the skull. Might as well make it a utilitarian looking, if aestheticly not displeasing color.\\
basically, a small panel for interfacing the spinal taps to an external high-bandwidth source, for when the ubiquitous wireless data connection is too slow\\
A: a Pluralis trait, or is this a standard of sorts for the VS universe?\\
or rather Klk'k habit?\\
T: It's mostly Andolian hardware, but connections of various degree and make are common in other groups\\
A: yeah, andolian--sorry, I may be liking the homo sapiens something signature a bit too much :-)\\
T: The Protectorate citizens have the highest and earliest implantation rates\\
With the Andolians and Purth having a 100\% implantation rate (the Purth are all heavily cybernetically augmented - but then they have to be to be sapient in the first place) and the Klk'k have a very high implantation rate\\
well, The vast majority of the Andolian population is distinguishably Pluralis :-)\\
so it wasn't an inappropriate phrasing\\
Deucalion actually has a number of augmentations, but most aren't externally visible\\
A: you'll have to tell me about those some time or other, since I do think it's my duty to know the characters I draw\\
T: assuredly :-)\\
hmm yeah, we'll have to work on hairstyles at some point, but anyone who's seen the various incarnations of my mop would know I'm not an authority on {\em good} looking hair\\
some other thoughts that came to mind\\
A: I have to cut his hair shorter, according to your description. does he wear, I dunno, braids? some sort of mohawk (please tell me he doesn't)? shaved patterns? there's lots of options to choose from, or combine.\\
T: his main concern would be that his hair doesn't interfere with his helmet, while still showing that he {\em has} hair\\
(the Shapers having a lack thereof as a distinguishing characteristic, thus his hair as a distancing feature)\\
I'm seeing hair that's short enough that he doesn't style it much\\
a close cut, somewhat unruly mess\\
A: ah,, that's simple enough. a bit of a manga mess over short hair.\\
no greek style curls\\
T: well, perhaps the hint of such on the top\\
waves that would become curls if they were to grow long enough\\
A: I'm taking note.\\
this is a very productive meeting!\\
T: basically, on the sides, the hair shouldn't jut out any more than the ears do\\
and the top would be somewhat more amenable to tweaking based on aesthetic issues\\
it'll be a different version of "helmet hair" than is normally implied :-)\\
A: so he's a bit vain, he he--is he a ladies' man, or a man's man, or both?\\
T: well, self-maintenance relative to some societal norms isn't something I'd label quite so harshly as vain\\
but clearly conscious of his appearance\\
he'd have to be, if not in the traditional sense, given that he grew up among aliens\\
A: I'm looking forward to know about that, too\\
T: He's wired fairly hetero, but growing up among Klk'k is it's own deal with respect to sexual mores - it's certainly not judgemental in the current western schema\\
so, definitely not a Man's man. I'd avoid the label of ladies man on the principle that, while he's sexually active, and not currently involved in any long term relationships, neither does he prioritize activities towards garnering female companionship\\
But, not averse to female company, no\\
The more interesting thought than gender orientation is species specificity :-)\\
He's specific to humans (of all subspecies) and Klk'k.\\
A: and so was his sister, from the looks of it\\
T: well, his "sister" {\em is} Klk'k\\
he's adopted\\
A: I knew he's adopted from the monologue, didn't stop much to think about the sister\\
T: Interspecies relations are still outside the mainstream. Moreso for certain pairings than for others, moreso for certain groups than for others.\\
Clearly, any such pairing is non-reproductive, and the physiological issues presented that govern any physical relating (let alone alien psychological issues) are non-trivial\\
A: and when you least expect it, you see the most gorgeous shaper dating the ugliest rlaan.\\
T: well, any pairing with a Rlaan would be very hard\\
A: just kidding--I know about their two-strata society\\
T: actually it's because they aren't Oxy breathers, and require entirely incompatible temperature and pressure ranges\\
A: methane breathers\\
T: and who wants to dance with a Rlaan-Briin in an encounter suit, when he has to keep making stops to recharge it ;-)\\
anywho\\
clothing\\
A: here's were you start defining klk'k (at least their apparel ;-) )\\
T: actually, not yet (at least until I get to the more formal-wearish :-) )\\
I'm seeing the default Deucalion casual-wear leaning towards under-clothes for his flight-suit\\
non-loose tank-top-esque top\\
non-loose shorts\\
flight-suit boots\\
A: socks?\\
T: no, the flight-suit boots would cover that. More likely just a couple of soft thin bands to pad above-ankle region from the rim of the boots (low boots, boots rather than shoes solely for sealing purposes)\\
depending on climate and such\\
he could be wearing the bottom half of the flight-suit\\
the flight-suit isn't very thick, and is form-fitting and stretchy, almost clingy\\
in contrast to the exceptionaly loose and baggy nasa space-suits of today\\
A: ok, for form-fitting flight suits we're talking entirely different technologies\\
yup\\
T: yes, different materials science\\
A: It's clear that I should have talked to you before doing those fixers :p\\
T: well, a couple of them :-) But clothing will vary greatly amongst factions. Also, it's a flight suit - it's not intended to be worn for hours on end in space on a regular basis - it's designed to keep you alive while flying, and safe in the event of hull breach and such\\
it's not designed for extensive repair-work or prolonged EVA\\
that, combined with materials advances, makes it feasable to have a suit that does not encumber the wearer nearly so much\\
although it's still cumbersome\\
more like a stretchier wetsuit/drysuit in hinderance factor than a space-suit\\
so basically, for vacuum wear, Hard-Suit >> Long-Suit >> Flight-Suit >> Skin-Suit >> anything else\\
well, Skin-Suit/Environment-Suit\\
err sorry scratch that\\
Flight-Suit/Environment-Suit\\
The Flight-Suit is optimized for Vacuum, whereas an Environment-Suit is optimized for one or a range of inhospitable environments due to biologicals, radiologicals, atmospheric chemistry, low pressure, or temperature range\\
(high-pressure needs a Hard-Suit)\\
Long-Suits being similar to the Flight/Environment models excepting being designed for extended periods in said environments\\
A: so how many in total? I'm confused. Just two, the skinsuit and the env suit?\\
T: Skin-Suits are vacuum rated, but offer little physical or radiological protection, and are valued more for the hermetical seal than anything else\\
no, several classes\\
A: ok, how about the hard suit?\\
T: Hard Suits >> Long Suits >> Flight/Environment Suits >> Skin suits\\
Hard Suits are completely self-contained\\
they have external manipulators (fingers being subject to pressure crush issues)\\
and are designed for exceptionally hostile environments\\
crushing pressure, massive radiation, highly corrosive atmospheres\\
A: ah, EVA pods of sorts\\
T: yeah\\
http://www.nuytco.com/exosuit.html\\
+1200 years\\
well, that's actually more like a Long-Suit, but you get the point\\
EVA Pod\\
Whereas someone wearing a Flightsuit is going to look more like much more like they are wearing thick neoprene or some such\\
but, as to his clothing, for casual wear, it's things he doesn't have to take off to put his flight-suit on\\
now, for more formal-wear\\
A: go on\\
T: firstly, the Klk'k are somewhat anthropomorphoid insofar as they have 2 arms, 2 legs, are bipedal, and have heads.\\

Klk'k style uni-gender semi-formalwear tends to be variants on a loose, sleeveless, single-piece garment that runs completely flat across the front, tapers slightly out from waist down and is slit in the back somewhat below the waist \\
ignoring the lack of arms, the closest thing that comes to mind in human clothes is an Indian garment I saw in a fashion show once\\
it continues down to slightly above the ground\\
A: no provisions for neck or collarbone?\\
I take that, despite its simplicity, it's ornate\\
T: not entirely sure what you mean?\\
the neck/collarbone part\\
it's sleeveless, not strapless :-)\\
A: ah\\
T: there is fabric straight from shoulder to neck. but no collar\\
the rear opening is convenient for the Klk'k as their legs bend opposite ours\\
The ornateness is highly restrained, with patterns being limited to the edges and waist area, running in thin seams around the garment\\
the prime regions of Ktah are quite humid, and ostentatious layering would not have been comfortable\\
informal Klk'k clothing tends towards a short, loose skirt, with tops varying by region\\
A: but our guy doesn't walk around showing his buttocks through this slitted garment or does he?\\
T: no, the slit starts lower than that\\
and he wears undies\\
when such is called for\\
nudity not such a big deal in Klk'k culture. The coverings are as much practical and protective as shielding from the public eye.\\
pockets, belts, places to put or hang things, footwear, clothing to prevent scrapes and scratches to various areas\\
A: they're a practical bunch, these klk'k.\\
T: well, there's also clothing to show respect\\
show allegiance\\
traditional body-paintings\\
tattoos\\
A: that's a chapter on itself, I take\\
T: sure\\
they aren't anti-decoration, or even anti-clothing\\
they just aren't obsessed with covering themselves up with the local cloth equivalents\\
A: does Deucalion wear any tatoos, ritual/cultural marks?\\
T: yes\\
He has a Tk'latl tattoo on his upper left topforearm/shoulder area, with annotations denoting his rank and record in Amakakt (the martial art heavily featuring said Tk'latl)\\
http://www.ocf.berkeley.edu/~jackass/sket ches/klk'k-emblem.png\\
the Double-bladed staff (seen sheathed and cradled in the horn in the sketch) is the Tk'latl\\
A: written characters? I can come up with an alphabet/syllabary/pictogram set.\\
or just make up the marks in the forearm :-)\\
T: Not written characters\\
A: the shape of the staff itself?\\
T: the ranking is above the Tk'latl, and consists of a series of vertical bars of different color, denoting increasing ranks attained, from left to right\\
A: and in Deucalion's case...\\
T: the history of the matches is recorded in colors corresponding to the rank of the opponents, and lies below the Tk'latl, with vetical bars for victories and horizontal bars for losses\\
Deucalion has achieved the 10th of 12 possible ranks\\
A: no failures?\\
T: none against lesser or equally ranked opponents. A couple tournament losses against mid-ranked(4,5) early on, a couple challenge tournament losses against masters (11th rank) later on.\\
A: no horizontals then.\\
or tiny ones?\\
hehe\\
just joking\\
I can picture him now far more clearly\\
How do we go about the story for the comic?\\
T: well, horizontals still. Defeats still count as defeats :-)\\
A: (not changing subject, just bringing up the issue for when it's appropriate)\\
T: his other shoulder has calligraphy for each of the family names of his adopted parents, and the chosen name of their bond set\\
I don't have a clear idea about exactly what the Klk'k written languages will look like, and it's supposed to be calligraphy and they're all given names, so feel free to make up something\\
A:family names as in jewish tradition? "jehuda son of moses son of abimael son of samuel son of ..."?\\
roger\\
T: not quite\\
the dominant culture for some time uses a strict two-name scheme\\
when a bond-set is formed, they choose a name for themselves\\
A: ok\\
T: and that is the bond-set name for those children raised by that set\\
if the set changes, through addition, the name may be changed or it may be kept, but the children will retain the old name, unless very young\\
if the set changes through attrition, the name does not change\\
in order to honor what was, even if it is no more\\
so, you are known by your bond-set name (the name of those who raised you) and your personal name, usually given in that order\\
so it's not lineage tracing beyond one generation\\
A: are bond-sets two-partite?\\
T: no\\
A: I imagined not :-)\\
T: 4 is normal\\
2 is somewhat odd, 3,5,6 aren't considered odd, but are less common\\
A: sounds... complex\\
T: more than 6 is generally considered somewhat odd\\
well, the easiest way to think of it is as if a small commune all married each other\\
A: BTW, I've done reverse-jointed legged aliens before--see if you like the way these look-- \\
\begin{verbatim} http://www.haeggalaxy.com/haeggalax y/modules.php?name=Content&pa=sh owpage&pid=3&page=4
\end{verbatim}
still, two sexes?\\
T: yes\\
seen that comic actually, I read it when you posted a link to previous work :-)\\
the Klk'k are built a bit differently\\
A: then saga of ryzom came and stole my idea of a tree-world :p\\
lol\\
T: different proportions, more hip splay, longer, flatter feet\\
good jumping legs\\
not good things to be kicked with\\
disproportionately large leg muscles on an otherwise slender frame... but I digress slightly\\
A: heh, it becomes VS lore the moment you type it, and I need all of the data I can have on those guys\\
well, that should be all for today--g2g\\
T: other attire for Deucalion, right armband signifying his rank in the Protectorate Fleet and non-duty status\\
(depending on where he is, this may or may not be appropriate attire, but he has one)\\

(Further conversation excerpts (edited) on similar topics)\\

T: looks too young now, or more accurately, too inexperienced. Especially the eyes, especially in the profile sketch.\\
Alexbetzone (2:21:07 PM): more knowing eyes... check\\
I found no guidelines for eye color. What color are they?\\
I'll fix the hair, no prob\\
T: Dark green eyes\\
hair color should be darker\\
more navy-blue that looks black except next to black and less cornflower/royal blue\\
A: all right, navy blue dark--shiny, I guess.\\
T: doesn't have to be shiny\\
A: matte hair?\\
I know what you mean, just kidding\\
T: well, highlights make it perceivable as hair and not a spilled mass of indigo ink\\
:-)\\
A: yup--no superman spit-curl\\
any other corrections or additions? note I haven't tried the scar thing yet. I was going to place it near the jaw.\\
T: trying to come up with a good rgb approx for skin tone\\
A: I used the tone in your mockup, but for the sketch I've been using "bleached" colors so the line art is easily seen\\
I won't next time\\
T: yeah, the color at present is a bit light, and seems short somewhat on green\\
but, we'll see how it goes as things progress :-)\\
A: ah, too purple? would you prefer a more neutral tone?\\
T: just a sec\\
http://www.ocf.berkeley.edu/~jackass/sket ches/headproto2.jpg\\
A: I'm ... beginning to suspect that your name isn't Jack\\
T: quick photoshop paint-bucketing\\
actually it is\\
sort of\\
A): I mean from the url :-)\\
T: I figured as much\\
A: once again jokingly\\
T: :-)\\
I'm not averse to humor\\
sorry to butcher your sketch with the paint bucket\\
it's not a precision tool\\
A: eh, you just gave me a color scheme I needed. that you grok photoshop has made it easier for me.\\
T: glad to be of service :-)\\
A: same here--I hope the comic, posters, intro fmvs and whatever else help spread the word about VS\\
deserves a lot more attention than it has\\
 btw, there's talk about a logo every now and then but nothing concrete\\
T: My thoughts on a new tag line-esque phrase go as follows:\\
A: (ah, you must've read my post on the subject already.) ?\\
T: "Before Success must come Survival"\\
Vegastrike.\\
"The void beckons"\\
A: somehow I suspected "tales of the void" not to be final\\
T: Legends of the Void sounds like a name for an expansion pack :-)\\
"Play all the NPC characters you could only dream of being in the original!"\\
hehe\\
I can see the advert \\
with the above tag line\\
or rather, above above\\
Word on black "Before Success..."\\
Images of wealth, splendor, glory\\
word on black "Must come survival"\\
images and pounding sounds of labored breathing and heartbeats, screams of pain and battle cries, quick cuts of interspersed combat\\
A: don't mind me if I take this verbatim and screenplay an intro around it!\\
T: Sound cuts, spoken "And you are very small" Show EVA suit working on repairing battlecruiser in space dock, slow zoom out\\
Cue logo \\
A: which we are in dire need of\\
T: not sure what sounds to put here, something ambient, or maybe some voices in the background through static, or maybe.. not sure\\
pause for a couple seconds.\\
text and voice-over "The Void Beckons" (slight pause) between Void and Beckons in the speech, but not the text\\
A: background music: classical (such as Holszt's Planets), cosmic new age a-la Jarre, rock, VS theme...?\\
T: different for the different emphasis points\\
something classical would fit well for the success part\\
A: Hmmm, something baroque?\\
T: but the music the survival part should be percussion driven chase music, agressive, raging, scared all at once\\
brash, violent and jagged\\
no music at all for the pan out in space\\
conspicuous silence after the previous section\\
not sure what to do for the end music-wise\\
A: I suggest not music, but an undefined sound of "unknown aliens out there", sort of a low harmonic with just a bit of a shrill halo, or something along those lines\\
as if there was something mystical about this "call of the void"\\
T: or a low harmonic with a muted pulsing beat\\
if it wasn't "the void" I'd go for softly whistling wind :-)\\
something to play around with, for sure\\
A: you know, a quantized wind effect could work there too\\
aka "electronic wind", just manipulated for a more subtle effect\\
T: I can talk about the Klk'k some, if you're willing to deal with some ideas not yet full rendered from mind to either page or word\\
A: of course, and if you wish, my pencil is in service of helping ideas take shape--I could try to approximate something from your description\\
so you can refine, I try again, and so on\\
T: that was indeed my hope :-)\\
A: great!\\
T: so, here was my first attempt to draw a Klk'k skull http://www.ocf.berkeley.edu/~jackass/sket ches/klk'k-skullbones.png\\
and here's a poorly done profile (head is still skeletal here) http://www.ocf.berkeley.edu/~jackass/sket ches/klk'ksketch.png\\
and the ankle isn't right\\
but.. it's a start\\
average height range 4.5 to 5.5 feet\\
long, largish feet, reverse jointed knees, large easily splayed hips, excellent jumpers, thick, disproportionally long, muscular legs in proportion to generally much skinnier tops\\
wide, short, fair lengthed, back-bottom flanging head, with back facing nostrils at the rear base between neck and jawbone\\
jaw is wider than head on each side. because of angle, more teeth on bottom jaw than on top, bottom jaw teeth face slightly in, top jaw teeth face slightly out\\
mouth contains 2 tongues. has no connection to air passageway. has resonant "click" cavity in front top of mouth, behind and below the rear of the bone ridges forming the eye sockets\\
eyes are large and wide set, and the sockets prononouced in their bonyness\\
ears, such as they are, are 2 long curved ovoids, extending forward from just behind and below the top of the jaw joint to somewhat even with the top of the jaw joint and in front of the joint. Mostly flush with the skull, each ear is a series of cartilige-analog ridges protruding slightly out from the side of the head to focus sound into a central shallow curved trough, the bottom of which has numerous tiny folds of hair-lined skin atop a drum\\
smooth, hairless, thick, leathery skin\\
running from green-brown to brown-green\\
two thumbs on each hand, four fingers between\\
hands hang at about knee level\\
 as noted, nasal passages are at the rear of the head, connecting to a common tube inside the neck and providing the sole breathing route\\
the real trick with these guys is to not make them look like little green men :-\\\
A: ah, leave that to me\\
:-)\\
T: their anthropomorphic features got them in serious trouble with the Lightbearers\\
the Lightbearers saw it as a mockery of the human form and took religious affront\\
A: I'll give them enough personality to upset a KKK\\
T: you can see my inability to use perspective well here: http://www.ocf.berkeley.edu/~jackass/sket ches/klk'k-emblem.png\\
the center object is supposed to be a Klk'k horn\\
with dual nasal inputs that must curve around to the back\\
A: ah, you mentioned that this also goes on Deucalion's arm over his fighting training marks\\
T: but the forward tube and bell got reial wierded out\\
well, just the weapon\\
not the horn\\
the weapon through the horn is the Klk'k emblem\\
 the (notably sheathed) weapon :-)\\
A: bladed, shooter, spear, multiuse?\\
T: it's an old traditional weapon\\
bladed on each end\\
A: makes me imagine a trident\\
T: no, it's a single blade on each side\\
looks more like a demented double-oar\\
the blade is wide and can cut on all three edges\\
but is not blindingly sharp\\
except on the outermost edge\\
A: beveled near the edges?\\
T: yes\\
the sides are for cleaving, as with an axe\\
the juts are for piercing, because of angle still somewhere between an axe and a spear, and the outer edge is for slashing, or thrusting, but not against a heavily armored target\\
or rather, doing so may dull or chip the outer edge somewhat, as it is more heavily beveled\\
hitting with the side works for bludgeoning, but it's not aerodynamic that way\\
the "wooden" ones are semi-functional oars\\
although metal versions are far too over-heavy for that task\\
the truly traditional incarnations, carved from the (human termed) Obelisk tree\\
are better suited for being multitasked as oars and spades\\
ultra-modern incarnations are much lighter, and forsake the traditional cleaving approach for having all three sides terminate in monomolecular thick blades\\
tranforming cleaving into cutting\\
A: quite deadly\\
T: no one uses that in sport matches :-)\\
they use the Obelisk "wood" ones\\
monomolecular spade works well as an entrenching tool too ;-)\\
well, not that well really\\
cuts well, but doesn't carry dirt all that well\\
strength is all running in the wrong direction\\
anyway... ummm\\
that's a start on the Klk'k\\
any obvious questions right off the bat?\\
A: quite enough actually\\
yes, although on a different subject\\
T: oh, one more thing, lips extend back along jaws, for very wide grins :-)\\
have to really, at the angles the jaw will be moving at\\

<conversation wanders>\\

A: you've seen the new fixers. what's you opinion? I know that those are only partially similar to neoprene suits :-)\\
T: I like them\\
the externality of the small features is certainly appropriate for civilian suits, and most military ones too\\
the only thing I have any reservations about is the head/helmet for the proposed confed pilot\\
A: that's not the helmet, but go ahead\\
T: ok, that's what I was checking :-)\\
good\\
A: I haven't drawn any helmets now that I think about it\\
T: makes sense really\\
they're on the station\\
A: yup\\
T: most people would take them off\\
A: I'll use that as my excuse :-)\\
T: so, what then exactly {\em is} the pilot wearing on his head :-)\\
(the confed one)\\
A: combination head-gear (additional data feeds for the goggles), audio equipment, an additional level of cushioning, whatnot\\
T: sounds good\\
makes sense for most of the human groups :-)\\
but we can fairly safely assume that most of the pilots working directly for the confederation rather than in forces assigned to the confed are Purists or LIHW of fairly equivalent stock\\
A: well, could the headgear also be an option for those not wanting a socket in their head?\\
T: it's the only option for those not wanting a socket in their head ;-)\\
ell, excepting getting your head removed :-)\\
(but we'll ignore mechanist military pilots for the moment)\\
but yeah, you need to get the data one way or the other\\
A: the exoskeletal bits I imagined as meant to preserve the body from being bent grossly out of shape in high Gs or collisions--self-activating like airbags, maybe with some intertial dampening in them? of course the life-support layer is still below\\
some sort of support frame. is that still valid within VS techs?\\
T: no inertial dampening in the suit. it's generated externally to the pilot.\\
too big to carry around\\
A: so I need another explanation for the exo bits\\
T: so - two things\\
1. conduits\\
2. old-fashioned structural support for high-Gs (not enough to save you in an accident, but enough to make the flight more comfortable)\\
i.e inertial dampening is not a perfect thing\\
A: that'd explain the pilot having so much of it\\
T: especially the conduit issue,\\
you need a stable structure for things to flow through\\
A: how about multifunctional? both 1 and 2, and maybe some additional functions.\\
T: well, that's what I was implying :-)\\
A: ah, ok\\
has anyone come up with an explanation of VS's spatial distortion technology?\\
T: the details on how it's remarkably efficient to be able to nearly arbitrarily alter the geometry of local space?\\
 or "how do shields stop X"\\
A: the former\\
T: not really, and I've intentionally not pursued it, because I believe that, once you've decided that something is *magic* then it's best to not try to explain it until you really have to\\
now, for questions like "how do shields work" or "how does SPEC work" that seem related, those I've pondered\\
the underlying ability to be able to manipulate space-time that fuels both of those (among other things) I haven't gone into details for\\
that answer the question?\\
A: sure, amply so\\
oh, before I leave: should pirates have melee weapons showing/hidden in their apparel?\\
I was planning on a suit for them made for the show: barbaric spikes, armor plates, the works\\
T: might work for the more eccentric special chars, but in general, one would imagine a pirate would keep a lower profile in most of civilized space\\
A: so concealment it is\\
T: the primary non-ornamental melee weapons would likely be a shock-stick and the old-faithful sharp-pointy-thing\\
the sharp pointy thing purely for stabbing people in the back / cutting throats with\\
after all, bringing anything heavy enough to breach a hull is not going to be appreciated by security\\
but if you want to gut each other in an out of the way corridor... so be it\\
A: clothes to conceal small to medium size weapons, a hint of seclusion\\
T: yup.\\
because the bounty hunters aren't there just for looks :-)\\
and they're likely licensed to carry light weapons :-)\\
(of the ranged variety)\\
A: ah, so the brutish pirate thoughs that didn't have a knack for subtlety are extinct now\\
T: or have fled to more forgiving regions of space\\
Forsaken and Uln territories should have some ... interesting characters\\
A: ah, the stories they could tell :-) well, I'm off\\

A: there's not much data on the klk'k, and I'd rather not use too much creative freedom (most likely my picture of the klk'k wouldn't be very consistent)\\
I have your data on combat ranks, some on biology (sketches), mating habits and clothing\\
but nothing to really 'picture them' physically in my mind. how do you 'see' them?\\
 do they move slowly and heavily, or quickly like small reptilians and birds? do their skins resemble a lizard's, or a mammal's?\\
T: not quite either\\
more leathery, but not scaled\\
smooth\\
Moving freely, but with the constant potential for a quick, jerking, jump\\
Imagine a dignified dancer, but with too many cups of coffee and convinced he's being stalked\\
A: he he, that's very graphic :-)\\
T: the leg angles mean that they have to strut a bit to walk\\
A: so the legs extend backwards and sideways\\
T much more back than sideways, but far more splayed than ours are\\
I often think of them as creatures that came down from the trees, not like our ancestors, onto a savannah, but into a bayou\\
A: a bayou planet? I like these guys\\
T: planet, no\\
original habitat, yes\\
A: ok\\
T a common one as well\\
but not ... ubiquitous\\
that would be boring :-)\\
well, or dagobah :-)\\
only with more sunlight\\
I guess dagobah was more swamp than bayou\\
A: if we ever go into production design for this kind of thing, noz and I are gonna have a field day\\
T: :-)\\
A: I see a sort of 'lip' in the klk'k skull. what's it for?\\
T: which pic?\\
A: side view\\
heh, actually that seems to be the ocular cavity\\
T: yeah, somewhat pronounced ocular ridges\\
A: any special ability/feature associated?\\
T: they have no nose, so the first thing to hit them in the face hits them in the eyes otherwise\\
A: so how do they breathe? similar to aera?\\
T: no\\
A: thank you\\
T: rear facing dual nostrils\\
note the splayed jaw\\
A: swimmers?\\
T: they come up under and behind\\
capable swimmers, not ambphibious, but hydrophilic\\
A: very long feet, too. clawed, membraned?\\
T: the foot length is mostly jumping leverage, but it does make a somewhat decent paddle.\\
A: fast runners?\\
T: not incredibly - at least for distance\\
short stubby claw/nails on the feet, degenerated tree grippers.\\
A: of course. if the length of the feet was arched, then I would believe them to be sprinters.\\
A: I'm thinking the arms should be a bit bigger in girth than I drew them, but length I'm ok with\\
not too much though.\\
A: the double opposable thumb did make me curious\\
T dextrous\\
good strong grip\\
A: more than us I take?\\
T: A bit, the second thumb doesn't buy that much without additional fingers\\
but they'd have an easier time opening child-proofed medicine containers with one hand\\
basically, you can get grip+manipulate with one hand, but that doesn't make the manipulate part better\\
now, when just holding something, they'd have better stability\\
A: gotcha. just one eye though? no chance for independent maneuvering on each arm?\\
T: no, two eyes\\
look at the top view of the skull\\
A: anyway. independent sockets, of course? they can be inset in the ridge\\
T: yah\\
two distinct ridges actually\\
A: ah, I see now\\
must have confused yours with other stuff\\
T: jack.art-skill.clarity--\\
;-)\\
A: no, no, they're clearly distinct sockets, you're right\\
T: I think a key thing to keep in mind is the Klk'k have to be sufficiently anthromorphic that the Light-Bearers were infuriated by them, but never anything close to pity :-)\\

\subsection{A conversation on baselines, models, and playability}

P: I am pretty interested in making sure the player has some sensible ships to buy, though.\\
The way it is now, all the ships to buy are hardcore fighters, shitty, or giant freighters.\\
T: sure, but that's as much an issue of not having all the models we want as what each model we have should do\\
P: there's no middle ground, and no progression.\\
I suppose...\\
but making a good game is important too.\\
T: I agree\\
P: It doesn't really make sense to keep all the top quality models locked up.\\
I pretty much said "shit, we don't have an Llama +1 s"\\
T: (I've often been tempted to dump a few hundred place-holder lines into the units.csv and just assign a box as the model... but I thought better of it ;-) )\\
P: "what model looks good, and could fit some cargo in?"\\
"ahh, the admonisher. cool"\\
T: so you think the plowshare is too much of a jump from the llama?\\
P: I do. Well, I mean it is definitely close to the llama! but look-wise it is more towards the cargo-cargo side of things.\\
what if the player wants to keep on the fighter-cargo route?\\
a balanced one.\\
We really don't have enough good models to go around... that's the root of the problem.\\
So until that happens, I think we should try and find a creative way to satisfy the needs of the game, while keeping the integrity of the universe.\\
Maybe by double using models, massaging some things around a bit...\\
T: I'm having a flashback to "red slime, green slime, blue slime!"\\
P: a necessary evil...\\
some of the best games have done that.\\
T: watch out for them palatte shifted ones ;-)\\
P: Those are always more dangerous, yes.\\
The new upgrade thing lets players pretty much decide for themselves what they want the ship to be. Aside from mass, cargo, and flying characteristics.\\
So just massaging some of the admonisher's (or any ship's) core stats around so it could help fill a different role wouldn't really kill anyone.\\
you know what i'm saying?\\
T: well, it isn't really a civilian ship to begin with though, so I'd prioritize making sure that the milspec versions made sense.\\
I think I see what you're saying - give them lots of .blanks, and they'll build whatever they want\\
P: yeah. a lot of .blanks with a lot of variation in quality, shape, and color. and it should all fall into place.\\
I'll fidget the admonisher back in the original direction\\
T:so, as I said, I'm personally tempted to go the placeholder route myself\\
rather than the co-opting route\\
but either way the root problem is stil the same - insufficient model capital\\
P: I honestly don't see what that would add to the game.\\
yeah\\
T: it's hard to make the universe piecemeal\\
so, the ship I think that most suits what you were looking for would be the Forsaken's Scarab\\
but we don't have one\\
The Kafka is unarmed, the Reindeer is even more towards the plowshare side, and the only other things that come even remotely close are intended for roles as orbital cargo landers to provide interesting traffic for stations\\
so... \\
yeah.. not enough models\\
there are other things that we've been "making do with" for some time as well.\\
the Schroedinger is a scout, not an interceptor, and so on \\
The Goddard model will eventually be moved to something else when I manage to commission something that looks more... Andolian.\\
bleh.\\
So, the question from my perspective is, is it better to take an existing model+ship pair, and pull it away from it's intended and eventual role, and then rebalance again when we get more models and can shift around, or to steal/copy a model from an existing model+ship pair and use it to incarnate a ship whose role we desire but whose model we lack\\
P: number two.\\
duplicating art is lame...\\
T: so you mean number 1 then\\
P: but!\\
aha. but!\\
i mind farted for a second there.\\
anyways\\
but! it's an accepted practice to do it. \\
even in professional, commercial computer games a bit.\\
or... i don't know.\\
i'm out of brain juice\\
T: well, what seems to make some sense to me is to do the balancing based on ships that fill the role you're actually looking for, and then, if nothing else, we can always harangue artists for those most key unmodelled ships before each release and not spawn the rest, duplicate art, or decomission underused models for temporary assignment to more important ships (even if the models don't fit so well :-( )\\
but, whatever is chosen, I think balancing based on the ships we'll eventually have reduces duplication of work and the "don't have a model issue" can always be pushed out until we actually have a release\\
P: that's reasonable.\\
T: besides, maybe having a bunch of placeholders in CVS will motivate artists to help make some more art for the things they keep having to see ;-) (or not)\\
ok, so with that in mind - how about we try to perhaps make sure we have the set of ships we really want to be working with :-)\\
P: that seems like a step in the right direction.\\
T: so I updated the brief descriptions to reflect the roles of the 8 selected ships. Only a couple of minor changes in emphasis (excluding the major change to the admonisher)\\
P: yeah, i saw the message.\\
T: so\\
llama: Venerable LIHW built armed light cargo shuttle\\
redeemer: Aging Luddite insystem fighter\\
admonisher: Purist light assault craft\\
plowshare: A top of the line Purist cargo shuttle\\
pacifier: Aging Purist heavy fighter/bomber\\
gawain: Main line High-Born interceptor\\
lancelot: High-Born heavy superiority fighter\\
dostoevsky: Andolian Protectorate mass production superiority fighter\\

P: those are better descriptions.\\
T: Thanks :-)\\
So one thing I want to make sure we have the same semantics about is what "interceptor" means\\
P: what's your take on the word?\\
T: designed to take out incoming assault craft\\
generally sacrificing durability, and enduring firepower etc. for accel and heavy first strike capability in order to be sure to engage and destroy hostiles outside of the range at which they can effectively damage friendly targets of importance\\
ot, however, a synonym for "agile, fragile light-superiority fighter"\\
et tu?\\
P: yeah, pretty much. interceptors intercept. that's what they do.\\
T: the VS ai priorities currently reflect this :-)\\
okiedoke. Just something I wanted to check because I've seen games where that really wasn't the case :-P\\


\section{Plot Outlines for Rimward of Eden ( circa 11007 CE )}

A conversation (edited):

rimward of where the THWON have returned to
in the madness that remains of them
back to where old memories took them

but the stories are all quite far apart in time
the one I want to attach to "Rimward of Eden" takes place several thousand years after "Upon the coldest sea"
indeed, several thousand years after "Foundering Inheritance"
which takes place hundreds of years after Upon the Coldest Sea

there was a struggle between the Ancients and their creators, TWHON
think Gods and Titans, only with a different outcome
The Ancients lost their lives, the TWHON lost its/their (it's hard to choose the better term) sanity, among other things
there were, of course, many different types of Ancient
diverse playthings crafted while the mind of TWHON was itself more diverse
many of the varied and bizarre devastations visited upon former Ancient worlds occurred after the struggle proper, after the residents were themselves all or mostly dead
and what was left of the TWHON was far from sane, far, even, from a semblance of intelligible thought
torn apart by a civil war among different aspects of a single mind
shredded utterly bashing itself against the small but sharp holdouts of the Ancients
TWHON is an appropriate name for them, for the aspects were not so much named as *the name*. Embodied aspects of thoughts, principles, ambition
But what is left is no longer a mind

D: don't suppose you've got history for what they were before and how they became that mind?
T: not really - that predates even their own knowledge, to some extent
it happened a *long* time ago
the Ancients certainly didn't know the details
part of the reason their libraries (some of which continue operation in the void between stars) are interested in watching groups such as the Andolians
pondering how a life form evolves from muck to Godhead
D: cool
T: but for an approximate date, let's say that the ancestors of the TWHON became the sole owners of the entire galaxy at least 1 billion years ago
what may or may not have co-existed prior to this is unknown
how many species they initially represented is unknown
what they became was very well known to the Ancients, and not really much at all known to the younger species
I've tried to keep details about the TWHON out of wide public distribution
D: which you've done very well ;-)
T: a developers-only section would be nice... neh, whatever
Some things are best not served until thoroughly cooked
D: hehehe, indeed
T: but, I'm happy you think it a worthwhile yarn that I'm spinning
D: ya, it sounds sweet :-)
T: how's the plot for Black Paralysis coming these days, btw?
D: the plot is just about as murky as it's every been ;-)
T: ok, well, I was jotting down some things in the timeline, and that may be of use/interest to you at some point
D: that may well be a very good idea :-)
T: so, basically, I see Black Paralysis as potentially being a really good setup piece for all the glory, suffering, and devastation that comes in Foundering Inheritance
with the title being an apt reference to our inability to move quickly outside of the jump network, which, by the time it takes place, is pretty well hemming everyone in (the Aera were just unlucky enough to be in a corner and find it out sooner than most others)
D: hey! that's like one of the many meanings I actually thought of :-)
T: namely, the discovery of the "on-ramps" out of our section of the galaxy
and out of our section of the jump network
which.... seem to be blocked off
this, of course, is of profound interest to the remnants of the resisting Aera
and sparks some turning points in Human-Rlaan relations
amid some power shifts internal to the Rlaan between anthro-philic and anthro-phobic elements
mostly opaque to the casual human observer
an opacity not to our benefit
D: okay, you've just summed up basically everything I had worked out so far (and then some) ... neato :-)
T: but ultimately not to theirs (but not until Foundering Inheritance)
Foundering Inheritance will feature the launching of the fleet of 10,000, the joint expeditionary force, a grand symbol of of unity, progress, and optimism 
it will also feature the near destruction of the entire Rlaan species
both of them ;-)
D: hehehe, howso?
T: there are multiple on-ramps
they have to be opened from both sides
the expeditionary fleet was sent into one
but the Rlaan had their own plans for one they didn't bother telling anyone about
unfortunately, while the expeditionary fleet went through something unlocked due to ages of neglect
the Rlaan opened something unlocked because the other side was waiting, and hoping for someone to unlock the far side
oops
D: heh, unlucky
T: insufficient precaution, in many ways
over-trust of their own
relative to the efforts at the joint gate
where cooperation bred sufficient mistrust
D: that doesn't stike me as an overly rlaan trait though (overtrust)
T: but of whom?
they trusted themselves
they were betrayed by themselves
unwittingly
hubris
D: trust in teh benign unknown then
they seem to have always approached new contact with caution
T: they didn't know they were making contact :)
D: ya, but surely they would have thought of the possibility?
T: oh, yes, they did
but that wasn't what screwed them
they didn't know they were making contact *while they were making contact*
D: oh
T: they didn't think far enough outside the box to understand what happened before it was rather late in the game - a somewhat more Rlaan trait
D: ya
T: but yes, bad luck as much as anything else
had it been the joint venture going there, it would have been disastrous, but less likely cataclysmic
they got greedy and paid for it dearly
as did most everyone else
pay for it dearly, that is
could have been even worse
except that it got worse ;-)
but in a way that helped those further away
D: very cryptic :-P
T: That which was overtaking the Rlaan attracted the notice of the remnants of TWHON
not that it knew what they were
not that the Rlaan really understood what it was when it came through
but the nano-plague remembered
it remembered very clearly
for the first time in a very long time
it fulfilled its intended purpose
D: ooooh, nice :-)
T: now, the conclusion of this part will intentionally leave a few loose ends, but make clear what groups are still around
it will therefore be somewhat surprising to view the situation at the beginning of Rimward of Eden
(if one has been following events)
because, in the long interim between the two, much seems to have been both gained and lost
the protagonist in Rimward of Eden is actually an Aeran youth
on a planet of subjugated Aera ruled over by humans, themselves clearly fallen from some greater height 
upon further inspection it will become apparent that interstellar travel no longer appears to be occurring
D: interesting
T: As the protagonist struggles for his own survival in a landscape of standing buildings and collapsed societies, powerful artifacts and abject poverty, he will end up seeking the aid of an ancient "demon"
(of course, nothing of the sort, but what do they know?)
whose aid will end up transporting them and others met along the way on a trip that opens their eyes (and ours) to what has become of our stretch of stars
filling in some of the pieces in-between, will be the story of the fleet of 10,000 which ends up stranded (relative to where it launched from) by the events concluding Foundering Inheritance
but this story takes place a long way away, and is a story of what happens in our neck of the woods only though inference, and the story of what happened somewhere else, a long time ago
D: :-)
if this were a set of novels, I would so own the series :-)
T: as a set of games, I don't envision all of them being well suited to being flight-sims, or at least not in any traditional sense
D: it seems to be most of them won't be
T: well, Icarus Descended would be best served Elite-like
moreso even than Upon the Coldest Sea, in that it *is* an often lawless, expanding frontier
much more "western"-esque
makes all the "space-is-for-libertarians" crowd happier... until they remember what it all turned into in VS - freedom begat monopolies, totalitarian states, fascist intrusions, and religious extremism as well as democracies, progress, and personal growth
There's also the story of the Fraternal War (aka. the war between the Andolians and Lightbearers) that I think has some good stories in it. From a Klk'k perspective, I'd go with "The Stars are also Pyres" as a good proto-title
that could play reasonably well as a mission-based flight sim
although, there are some ground elements that are more interesting
although it perhaps makes more sense to just experience them, rather than influence them
And then there's always the best fodder for an FPS - "Simon says die"
about the Simons
D: hehehe
T: did I tell you about the Simons?
D: nope :-)
T: think simon wiesenthal meets "the punisher"
From a Klk'k perspective
D: neat idea :-)
T: anywho, so those are the broadest outlines of where I see story points of interest in a ~9000 year spread of time in the VS future history
D: ya, it sounds really cool :-) you've certainly put a hell of a lot of thought into it :-)
T: well, I wish I'd put as many hours of writing into it ;-)
at least gaim archives conversations, so I can point and grunt when people ask again ;-)
D: lol
T: I think Rimward of Eden would be best as an adventure game of sorts
whatever the interface, that's the genre it seems most part of
even if the mechanics involve a first person perspective
I think, especially in a first person perspective, it might be interesting to be an Aera
D: definitely :-)
foundering inheritance doesn't really fit anywhere though in terms of comp games ... it'd be a great novel, but there's so much that just couldn't be conveyed in just one tyupe of game
T: well, maybe it doesn't make sense to just make it one game then :)
D: touche
T: but... given how long its taking us (admittedly at very-much-part-time-pace)
to do one installment, I'll worry about getting the universe in shape first
and then how we're going to present it
because there *are* several key points that do map to tangible genres
the other thing, is to look at one of the things I really want to do with VS:utcs
which is, to have a very flexible progression of "little story" in the scope of a much less flexible "big story"
which the character doesn't so much influence, as live in (the big story, that is)
Note that Deucalion is not the linchpin for 9000 years of VS history
D: course not :-)
utcs is just part of the story from his perspective
T: well, given that he hadn't been created yet, it'd be hard for him to be much influence on Icarus Descended ;-)
D: hehehe
T: and, unbeknownst to him, he did play some role, though through little fault of his own, in the timing of some events in utcs ;-)
which is to say, the role he played occurs befor utcs proper
and hence can't be screwed up by the player - then again, it'd be pretty hard to do, as the only required action is (more or less) his existing at all 
Deucalion is a remarkable being, in that he's actually an apology
Deucalion is a library's way of apologizing for killing an exploration crew some decades prior
His role in the timing of things entirely being an issue of getting the AI quorum pondering what built him, how, and why
and the effect that such ruminations had upon the rollout time for the "grandchildren"
sometimes, it is enough to know something is possible
that alone can make a difference, even if the particulars are beyond reach
a nudge, a narrowing of search, a path otherwise not taken, that leads to a slight speedup in something else, itself long in the making, long before Deucalion
D: cool :-)


\section{On the Fall of the Ancients and TWHON (NOT COMMON KNOWLEDGE)}

There were, as you assumed, more than two species of Ancients - in fact, I'm fairly sure it is mentioned somewhere (although I can't recall where, and if I can't, then... ) that there is evidence of interactions with at least six other groups of Ancients. The two in question were just the locals, and their domain was demarcated by the locked gates, an imposition of the TWHON. The TWHON, whether the Ancient group in question arose more or less naturally to a meaningful existence, or was created entirely from scratch by TWHON whimsy, were the creators of all of the Ancient groups in that the molded them and shaped them to their own designs and for their own reasons. Had their era not passed, there would have come a time when, whether directly or by Ancient proxy, the TWHON would almost certainly have manipulated Humans, Rlaan, and Aera alike for whatever motivation struck them at the time - and, if by odd chance we had remained sufficiently insignificant to escape the notice of the TWHON, the local Ancients would almost certainly have had their own games to play, more likely than not at our eventual expense. There were, to distill the essence of relevant groups, only the Ancients and the TWHON, as no other groups were given license to develop.

The downfall of both groups was to come from a great indecision within the mind of the TWHON. As the Ancients progressed into an early post-technological stage of development, certain aspects of the TWHON mind no longer saw it proper to use them as playthings and experimental subjects (both of the former as groups, not individuals - the TWHON didn't do "alien abductions" they just started massive interstellar wars, conducted xenocides, created plagues, monsters, new Ancients, challenges, rewards both equitable and not...  standard god-like-being stuff). To keep things brief, and use metaphor and analogy (though it leads to an incomplete description), one can picture this all culminating in an eventual Ancient revolt, assisted by elements of the TWHON mind that, rather than being squashed, instead set off a "civil war" within the TWHON mind, spilling over into the TWHON bodies. The defensive assistance rendered by the pro-Ancient TWHON lines of thought against their urges toward continued usage of the Ancients as inconsequential entities, would eventually become very well known to the extant species (and cause many later species to cease to be extant) as the "nano-plague." A majority of the Ancient groups joined the revolt, though some continued to fight by proxy for their masters.

One decisive battle would prove to be the beginning of the end for the era of TWHON and Ancient alike. On one of the two research planets in what is now the Uln home system, indeed, on the planet that is now a noticeable debris field in the Uln home system, research was frantically being conducted on how to reinforce the allied lines of TWHON thought at the expense of antagonistic patterns withing the TWHON mind. The future Uln homeworld was evacuated and the proto-Uln abandoned. Fleets of moon-sized Ancient craft, a fragment of one such eventually becoming the Sul-Gatwa high-castle, and numerous TWHON bodies gathered in the system to defend and participate in the ongoing research. An armada of TWHON bodies attacked the system, and prototype device were activated. The battle unleashed enormous devastation upon both fleets, but the TWHON-mind-altering devices were to prove far more lasting in the devastation they were to unleash. In addition to cognitive dissonance increasing within the TWHON mind from the operations of the mind-altering devices, the battle was sufficiently fierce that TWHON ideas, and thus Names, were dying along with TWHON bodies. These deaths echoed, and then reverberated, and then fed back and amplified on the devices, burning themselves into, and by turn burning out the TWHON mind. As the battle proper neared physical resolution, the forces allied on the side of the Ancients' liberation looking to have gotten the better of the engagement, though the victory would likely have already been Pyrrhic in the longer term, the TWHON mind sank below the threshold of sanity, all Names becoming muddled and losing sufficiency of form (the TWHON mind already having been many times weakened by prior TWHON-TWHON engagements). What moments ago were their supporting deities now turned on the Ancients in the TWHON slide from supremacy and, along with the remains of the invading TWHON bodies, themselves equally deranged, slaughtered every Ancient in the system and destroyed, too late, the planet on which their downfall was birthed. The Uln homeworld was spared a more sterile fate only for the hurry with which what remained of the TWHON mind wished to distance itself from a place of suffering.

What had before been a war, if a galaxy-devastating one, became a cataclysmic spectacle of heretofore unrivaled savagery, devoid of rhyme or reason. As the TWHON mind degenerated, the Names of Rage, Confusion, and Suffering fared better than many, and were allowed to greatly influence the actions now being undertaken by the TWHON bodies throughout the galaxy as they began to purge every system of Ancients of every kind, revolutionaries and loyalists both. It was in this period, not during the war proper, that the slag worlds were created; the great overkill measures of boiled atmospheres, muted suns, melted crusts, and shattered worlds left to re-coalesce into the not infrequent debris clouds seen in UTCS era systems were not the actions taken by victorious armies upon their foes, but by a great singular mad mind, fragmented and devolving, lashing out in sometimes self-annihilating fashion (see: worlds rendered uninhabitable by what would appear to be prolonged bombardment by large impactors) at anything that could be detected by its increasingly twisted perception. Every living Ancient in every system on the jump network was exterminated. Every gathering of Ancients in systems off of the jump network was obliterated. What was once TWHON hunted the Ancients, and in finding and annihilating them, found the occasional glimmering shred of purpose to its new existence. All that remained of the Ancients were arks and tombs, drifting alone in the relative safety of the void between stars. When it could no longer find anything to hunt, the TWHON bodies wandered, some disassociating, some taking to slumber, some few wandering beyond the edge of our galaxy, to slowly plough the deepest of voids toward ambiguous end, and a great many retreated to the warm embrace of the old and dying stars far coreward of our portion of this galaxy.


\section{Events in Foundering Inheritance Time Period (HASNT HAPPENED YET)}

One of the key points about the Foundering Inheritance era mentioned in the conversation concerning the overall VS universe timeline is that the Rlaan do not realize they are encountering a new alien entity. The destructive force that renders the domain of the Rlaan Assembly broken and the Saahasayaay nearly extinct is first encountered as the local variant of the nano-plague on the other side of the locked gate (the expidition of the 10,000 finds no local nano-plague, as the Ancients in that region had been supporters of the status quo) in the Saahasayaay home system. As the variation between observed nano-plague entities in locals space was greater than that between the two spaces, seeing more of the ubiquitous nano-plague on the other side of the locked gate was seen as mildly interesting, but generally unremarkable. It may have even been somewhat unremarkable, save for the other-side nano-plague recognizing the symbiotes in the Saahasayaay (see wiki description of Saahasayaay life cycle) and activating in a decidedly organized fashion. It is no coincidence that the habitable worlds of the jump network are disproportionately suited to oxygen breathers, and it is no coincidence that near the Saahasayaay system there are several other chlorine worlds, and near the Rlaan homeworld, several methane-ammonia systems, and another locked gate. These areas were provided for neighboring Ancient groups, resident across the locked-gate boundaries. The symbiote in the Saahasayaay was a tool of one such neighbor, and the other-side nano-plague, another tool, recognized its kin, even in its kin's damaged state. The other-side nano-plage effected changes to fix the symbiotes, allowing the other-side nano-plague (hereafter OSNP for brevity) to use the Saahasayaay as a conduit for information, and then for dissemination of the symbiote fixes back to the Saahasayaay homeworld. The eventual goal of both OSNP and symbiote was simple, if vain and likely futile: to prepare the way for a return of their long-dead Ancient creators, existing currently only as dormant information. While the OSNP increased its activity, building progressively larger colonies, the colonies macrostructures, and the macrostructures becoming macroscopic machines themselves, it remained resource limited - the immediate region of several star systems was quite barren, strip-mined in its hey-day during the Ancient-TWHON war, and then ravaged in the aftermath, and it would be some time before the OSNP would be able to produce drone ships either as an end product or to transport goods from richer systems. Neither could the OSNP act directly in our region, as our own nano-plague would react negatively to it if it were to try to expand. Instead, the erstwhile-Saahasayaay (not truly Saahasayaay anymore, but merely avatars for their finally flourishing symbiotes) staged a revolt, taking numerous Rlaan civilians as hostages, knowing this would delay the Rlaan response long enough for their ships, now crossing freely into the other-side to be upgraded by the OSNP - if not yet to anything resembling Ancient standards, then enough to be a great surprise to the Rlaan when the time for combat was to finally come. 

Bargaining, in a very uncharacteristic way for Saahasayaay (this itself already greatly disturbing the Rlaan), for the safety of the Saahasayaay outside of the home system with the lives of the Rlaan Workers, the ex-Saahasayaay gained both more crucial time and powerful weapon: the Rlaan Workers were themselves modified by the OSNP to have an innate desire to sabotage, kill, and disrupt - while the Rlaan would check them for bio-weapons and such, the Rlaan mindset precludes consideration of Workers as themselves being instruments of violence, and so clean bills of health and belongings would see them released back into Rlaan society. In a move reminiscent of the battle of Puebla, the Rlaan forces charged directly through the jump-gate and the inevitable fixed defenses, rather than flanking with SPEC. The Rlaan suppression fleet met with horrendous casualties at the hands of the upgraded Saahasayaay vessels, and, the first glimmer that more than just a Saahasayaay ploy to escape Rlaan rule via the lock-gate was underway, upgraded vessels of remnants of the Rlaan expeditionary force itself (there having been some resistance in the Saahasayaay overtaking of the expeditionary force). Though unsuccessful in retaking the system, the attempt had bought the Rlaan valuable time, though they did not then know this, for the OSNP ramp-up would be significantly slowed by the damage to many of the already quite small number of vessels at the command of the OSNP and ex-Saahasayaay. Nonetheless, while the Rlaan re-inforced and re-grouped, planning to send an even larger force through, this time via SPEC, this remained a "local" issue, with news of the Saahasayaay rebellion being an event not shared with the human powers. However, when, shortly after returning to Rlaan space, the modified Rlaan Workers set about their assigned terrorist tasks, the entirety of Rlaan space was overtaken with hysteria and paranoia - Workers committing violent acts of terror, even if the actual damage was so small as to be trifling, and most of the Workers in question perished in the execution of their tasks, was so antithetical to the Rlaan worldview of the possible that it threw their entire society into gridlocked turmoil. This was to prove fatal for long term Rlaan aspirations, and to be a saving grace for all other species in the region, as it was a disaster now too large to keep quiet. Fleet movements that could have all directed themselves in a bloody, but likely ultimately successful assault on the OSNP beachhead, were curtailed, as the Rlaan, in paranoid meltdown, saw threats everywhere that the released Workers could still be, and held back significant fleet resources for use with the Rlaan Enforcers to retrace the paths and hunt down every one of the "abominations." 

When the second attempt to retake the Saahasaay homeworld and the lock-gate failed (even more poorly than the first, thanks to new waves of ships of unknown design), the fact that the situation was exceptionally dangerous became increasingly apparent to all parties. Joint efforts were undertaken to organize an interspecies response. As these efforts began, the first counter-attacks began to issue forth from the lock-gate. As time wore on, the enemy ships improved in design rapidly, if only slowly in number. Analysis of probable causes leads to the the gate in (formerly) Forsaken space from which the fleet of 10,000 left being locked from both sides, isolating both fleet and research colony from the rest of known space. Strikes are radiating further and further out from the lock-gate, battles are slowly worsening in per-ship losses, and the combined forces of the extant species are being repeatedly forced to withdraw to keep from being overrun. The situation is grim,especially as it is obvious that time is not on the side of the newer species. It is only by becoming much grimmer that the situation will improve. 

As the first wave of nearly-Ancient quality drone craft is completed and larger craft construction commences and continues, it is launched en-masse in a series of attacks against the Rlaan, both fleets and worlds, carving a vast barren region into the Rlaan Assembly's territory. However, this coordinated use of Ancient tech stirs TWHON fragments slumbering in the other-side, and the resolution of this conflict is set in motion. A single small TWHON fragment plows straight through into our region, bypassing the unprepared OSNP, and engages the drone craft. Though the fragment is destroyed, the drone craft are decimated in number and universally damaged. All OSNP and ex-Saahasayaay forces retreat to an expanded beachhead area in the systems near the lock-gate, the drones being recalled for repair and re-deployment against the stirring TWHON fragments in the OSNP's own region. Meanwhile, the presence of a TWHON fragment in our own region fully activates our own nano-plague (it already having a many hundreds of years head-start on the OSNP due to our own FTL travelling). Nano-plague factories begin defensive preparations against subsequent TWHON incursion. Reconnaissance of the beachhead proves difficult, and recon through the lock-gate, nearly impossible. However, it becomes clear that the preparations being made at the beach-head are for an OSNP/ex-Saahasayaay escape from their region, and no longer directly a pacification of ours - the OSNP are losing. Though drone-craft from our region have begun to appear in number, they do not cross over into the next region to assist - they still obey the long meaningless borders between their long dead masters. 

With the evidence of a distinct drop in craft from the beach-head area signalling a likely imminent collapse, the joint Human, Grandchild, Klk'k, Rlaan, Aera forces embark upon a massive suicide mission of genocide - having realized that the OSNP cannot operate freely in our region except through the ex-Saahasayaay, and that they could not hope to defeat the OSNP forces in direct engagement, they instead chose to exterminate the Saahasayaay hosts to the Ancient-designed symbiotes and as much of any construction infrastructure as they could manage. The strike was well-timed, and the tactic not one the ex-Saahasayaay had weighted with high probability, having been too colored in their view by lingering effects of their time in Rlaan service. The Saahasayaay homeworld was carpeted by anti-matter bombs even as the fleet delivering them was being savaged by OSNP drones. It was unclear exactly how successful the mission had been - very few craft returned, and there were too many unknowns as to other potential bootstrapping sources for the OSNP. However, only days after the raid, TWHON fragments broke through the locked gate, signalling the totality of the OSNP demise in their own region, and the entire Saahasayaay home system, when it was next visited, was found to be slagged. Whether through previous TWHON attrition, or superior preparation, our own dones were faring somewhat better against the TWHON fragments. Also remarkable was that our nano-plague took to using jump-point deactivation as a time-gaining tactic in fighting the TWHON fragments, which either could not or would not be bothered to reactivate the jump points and instead would travel through some more advanced SPEC-like manner directly between stars in the absence of jump points. Though the TWHON-nano-plague fight raged, the priority of the extant species remained the re-locking of the locked gate. The expedition charged with doing so was assembled as quickly as possible given the extreme losses all parties had already endured, and expected to endure again. 

Upon reaching the, now disconnected from the jump network, former Saahasayaay home system, they found no fleet waiting for them, instead, they found a single, small TWHON fragment body and a series of slagged worlds. Much to their surprise, the TWHON body completely ignored them as long as they remained distant from the lock-gate. When local drones engaged the TWHON fragment and it chased the drones out of the system, the expedition set up to lock the gate and retreated. 

Though the few TWHON fragments that entered our region were eventually defeated (the long-active nano-plague prevented local procurement of re-inforcements, that being the true key point of the nano-plague, the drones being entirely secondary, as Ancient fleets were assumed to exist at the nano-plague's creation) the TWHON-drone conflict made the area around the lock-gate unfit for habitation both through further destruction of worlds and severing of jump-links. 

At incident's end, the Rlaan were no longer the power they were, with many worlds destroyed, many more damaged, their fleet broken, and the breach of trust that started the incident a sticking point that would be quite well remembered in the coming period of rebuilding - one they would pay dearly for in control over their future, and one which would lead the Rlaan-Briin to societal dominance with the support of the Post-Human powers. Moreover, there was now a great pallor over the futures of all of the extant species, as it became clear that this could not be a lasting defeat of the TWHON - rather, the very stirring of our nano-plague, it's true purposes at last revealed, would undoubtedly bring more suffering in the future. The sword of Damocles would now rest over all of their heads, and it would clock-like sound each hour to pass of doom creeping forward while salvation remains nebulous.



d: simply that the 'cleaning up' of the whole mess seemed "easy"
(22:28:20) d: as in, besides the space fleets, the only real losers from the whole lot were the rlaan and the s*
(22:29:01) d: which didn't quite match what I thought led to teh later timeline you talked about
(22:30:07) d: but I get now that it was the long term events set in motion (ie the activation of the local nano plague) are what sets ruin to teh current crop of spacefaring races 
(22:30:42) d: but don't let that comment mislead you, melikes :-)
(23:06:05) t: yeah, the Post-Human powers didn't get their turf destroyed
(23:06:13) t: but their fleets were shredded
(23:06:19) t: I should make that more explicit
(23:06:44) t: most of the ships involved in the late action, even defending the Rlaan, weren't Rlaan anymore 
(23:07:05) t: there just weren't many of them left
(23:08:23) t: The sweep made by the OSNP drone craft was a bit understated
(23:10:00) t: We're talking, Rlaan needing to ask for help to clean up all the dead Rlaan bodies understated
(23:11:02) t: And the suicide run.... would be the largest congregation of extant species ships seen in a long time
(23:14:03) t: especially with a hyper-active nano-plague playing serious hell with production (bad tendency to eat some high-quality materials) although that would die down soon enough 
(23:14:39) d: cooly, that's some better sense of proportion ;-)
(23:17:23) t: that, and they weren't able to confirm that they killed all of the ex-Saahasayaay
(23:17:42) t: minor potential problem, that, over the next few thousand years
(23:18:02) d: as in, point for focus of paranoid delusions?
(23:18:24) t: that, and just because you're paranoid doesn't mean they aren't out to get you
(23:18:27) t: :)
(23:18:37) d: :-)
(23:18:41) t: closing the gate was intentionally anti-climactic
(23:21:23) t: it deprives the survivors of the solace of accomplishment, false or otherwise
(23:21:55) t: forcing them to face the unsettling reality that, at most, they've only delayed the inevitable
(23:22:22) d: point
(23:22:45) t: which, I think, is a nice note to end that chapter on :)
(23:22:59) t: condensed in form as it may be

One of the things that I should have mentioned more explicitly is that the above was only a description of what was going on in Rlaan space during this period. The events in Human/Post-Human/former-Aeran space are fairly important too, and brought all the more to a head because of the fall of the Rlaan - it is worth remembering that a key reason that warfare was fought in a "restricted" i.e. non-genocidal/collateral-damage-minimizing fashion in the UTCS era was the Rlaan intolerance for civilian body counts (so if you were going to butcher planetary populations, you had to keep it on the serious down-low). With the Rlaan gone, there's nothing but human conscience to prevent atrocity (which is not a historically viable solution). Add to this the tensions between human (Basically Purists and allied factions - the Forsaken still remaining distant from the affairs of the Confederation worlds) and post-human (The Andolian Protectorate (having expanded (via negotiated annexation) by this point to include the former Unadorned, Mechanist, and Shaper polities) and the Grandchildren) political groupings in what has become of the Confederation and the destruction of the vast majority of the Confederation and its constituents' military forces (worth noting that the majority of the ships on the "suicide run" on the Saahasayaay home system were civilian vessels hastily armed as cannon fodder due to a lack of remaining military forces), and you have a recipe for violent unrest, even if the human worlds themselves were not ravaged. Likewise, even before the actual destruction of the fleets, there was significant political maneuvering occurring within Human/Post-Human space concerning both the fleet of 10,000/other expansionst projects and scheming by various groups to position themselves to profit from what was initially seen as a minor mishap in Rlaan space.

To briefly summarize where things go from here:
Sensing imminent Protectorate weakness, the Shapers plot and execute a revolt. With internal stress between the post-human and human elements of the Confederation already near boiling, the Shapers hope to ignite a civil war with their revolt, believing that they will come out on top when all the dust has settled and no other group remains to stand against them.

Preliminary movements of the Shaper revolt involve prodigious use of bio-weapons, including morphologic virus packages aimed at Purist, LIHW and other traditional human populations in Confederation space. The Forsaken, the bulk of their population now in former Aeran space, are not targeted due to extremely low population density. Chief among these virus packages are ones that overwrite the germ-line DNA, causing erstwhile human parents to either run sterile or produce offspring with Shaper-designed genomes. Viral packages for the Klkk populations are more simply plague oriented, and, as with the human packages, are designed for stealth and long incubation periods. The Shapers have also been producing modified fungal strains that act as factories for Quickships, extremely fragile but extremely cheap in-system pilotless craft. The Quickships require engines and weaponry, but are otherwise selfcontained. As they are considered totally expendable, great liberties are taken with the safety, reliability, and sustainability of the weapons and engines produced for the Quickships  Quickships would invariably die from radiation and heat stresses in prolonged service, even if they were not engaged in combat.

As their bio-weapons begin to activate, the Shapers actively revolt, laying a surprise siege to Kubernan. However, their intelligence gathering proves mortally flawed when their attack on Hephaestus is insufficient to halt production of Grandchildren. The blockade of Kubernan greatly reduces the flow of resources into Hephaestus, but the failure of the Shapers to break the Grandchildrens homeworld means that they cannot readily press home their intended beheading of the Andolian Protectorate. 

The Andolian-led response of the Protectorate is swift and brutal. Having actually made some preparations for a Shaper attack back during the cold-near-war period prior to the Aeran war and the unfurling of the Grandchildren, the signal is given to activate a number of deep-space asteroid bases set up a few weeks SPEC from each of the core Shaper worlds. These bases will spend the next several days accelerating at maximum thrust before activating their SPEC drives and proceeding on a collision course.

Meanwhile, plague and the creatures dubbed murder-babies for their habit of consuming their mothers just prior to expected birth, the latter turning out to be an extremely rapid-growth form of Shaper Hulk, inflict terror upon the human populations of the Confederation. The Andolians, in their sterile compounds, and many Mechanists, devoid of the necessary pathways for infection, are not directly affected, although there are riots and violence in the off-worlder sections of Andolian holdings, and the Unadorned will find themselves devastated by the Shaper plagues. The Shapers embark on a widespread propaganda campaign, and use the promise of cures and vaccines as leverage to gain support from the human governments.  Several capitulate outright, and many more are overthrown by their own populations, most, at this point, having long preferred to side with the Shapers over the Andolian led Protectorate and their emblematically non-human Grandchildren. The Shaper revolt is now a full-fledged civil war.

After six centuries of existence, the Confederation is now dead in name as well as fact. The Rlaan are powerless to do more than watch in horror, and the Forsaken and Marked-Aera are hard pressed enough as it is just trying to keep any potential plague-bearers out of their space. The Uln bide their time, preferring to wait until one side is closer to victory before considering any benefits possible from backing one side or the other or pursuing territorial ambitions in the resultant power vacuum.

With the bulk of human space-naval forces already having been destroyed in efforts against the ex-Saahasayaay, the engagements seen are quite different from those during the Aeran war. The Confederation Joint fleet has completely disintegrated, with individual ships falling to one side or another of the conflict, or simply returning to the crews system of origin. Small numbers of ships, many of them conscripted civilian craft, or Regional Guard forces are often deciding factors in individual battles. Capital engagements are only seen around key worlds, and ground engagements are frequently fought between small forces among swarms of ambiguously allied civilians. Neither side engages in significant restraint, and the toll in collateral damage is staggering.

While the Shaper assault on Andolian space gains little headway, and the blockade on Kubernan is broken, the retreat of Protectorate forces to defend their own territory has left the Shapers and their allies a fairly free hand to attack and consolidate power in the rest of the former Confederation. In a move that signifies to all with sufficient understanding that the Shapers no longer consider mainline humans to be members of the same species as themselves, the Shapers deploy mind-altering parasites to ensure the submission of both willing and protesting conquest alike. Throwing the resources, both  material and population, of their vassals into the fray as cannon fodder, the Shapers are able to keep Kubernan and Hephaestus under constant threat of attack, forcing the Grandchildren to be deployed defensively rather than be allowed to engage in strikes against their own forces. With the fall of Sol, Bantam, and New Camelot, the core region of humanitys oldest colonies is almost entirely in Shaper hands, with the Purists, ISMG, and High Born polities in collapse.

Attacking through space ostensibly controlled by the crippled Rlaan, but in truth barely patrolled, the Shapers attempt to plague-bomb the Shmrn worlds, releasing a virus package designed to turn future Shmrn generations into Dgn. Given the widespread panic in the wake of the war, countermeasures are in place, and the effect, as intended, is more psychological than military. This act, however, pushes the neighboring Uln to believe that neutrality would, in the end, be no armor against a victorious Shaper entity, and the Uln throw in their (small) lot with the Protectorate.

This would be the peak of Shaper aspirations for dominance. Coinciding with the impact of the asteroid-base kinetic weapons on nearly four-dozen Shaper homeworlds, the Protectorate launched a counterattack spraying forth from Kubernan, spearheaded by a fresh crop of Grandchildren produced at Hephaestus. The Protectorate strike force handily defeated the vassal-ships surrounding the recent Shaper conquests. However, they neither charged toward the Shaper worlds nor attempted to liberate the conquered human populations. Instead, the Protectorate had come to the conclusion that any world already conquered by the Shapers was too polluted by Shaper bio-weapons, traps, and incubators (human hosts being used to produce new Shapers), and was safer cleansed than liberated. Using what would eventually be revealed as a set of bio-weapons of Rlaan origin, the Protectorate fleet embarked on their scorched earth \& flesh campaign, destroying every extraplanetary structure found, raining down orbital bombardments upon every exposed spaceport and industrial area, and leaving behind a cloud of extremely voracious organisms capable of rapidly degrading planetary human populations to manageable levels  especially given the Shaper efforts on every conquered world to make sure their own bio-agents could have mass effect.

Certain that they could easily best the Shapers in direct engagements, the Protectorate sought out existing and potential hosts within Shaper reach and exterminated them with extreme prejudice. Both Shaper and Protectorate sides had known from the beginning that there would be no negotiated end to this conflict  the vast populations of the Purist and LIHW holdings, however, had never anticipated this war, and yet were the ones doing the bulk of the dying, being killed by the 10s and eventually 100s of billions. The last contribution of the Unadorned before succumbing entirely as a political and cultural entity, having been devastated by the Shaper plagues, would ironically feature heavily in accelerating the demise of mainstream humanity. Following on from the Ancient library research that had led to knowledge about the locking and unlocking of the far-gates, the Unadorned had discerned how to temporarily disrupt normal jump points. The Culling fleet, as it would come to be known, used this new ability both to delay Shaper reinforcements and to protect their own rear. While the disruptions lasted only a day or two, that was frequently more than enough time for the fleet to crush the Shaper presence in a system. The support of their vassals pulled out from under them, and a third of their own planets now without an inhabitable surface due to the impacts, the outcome of the war had been determined, and only the shape of things to come remained to be decided.

The human population of the old Confederation no longer a potential threat-in-the-making, Protectorate forces throughout the entirety of their space rushed out from their defensive deployments and began attacking relentlessly. The rush came from the perceived threat of the Shapers fleeing out of the jump network, slinking off to where they may not be found for centuries, an everpresent ghost of a menace, leaving all the bloodshed for, in the end, naught in terms of safety. However, owing to some degree of confidence in their eventual victory, the cultural unity of the Andolians, and, perhaps moreso even than the other two, to not having the AI Quorum cease its infiltration of Shaper computing systems when the Shapers joined the Protectorate, the Protectorate had a much better informed covert operations presence in Shaper space than the Shapers in the Protectorate.

The Shapers had not begun work on their escape efforts until after the Culling fleets offensive began. Though the preparations were still ongoing, the distributed nature of the Shaper efforts made it unlikely that sabotage would sufficiently slow the progress to allow Protectorate forces to reach all systems before an exodus could occur. Rather, the Protectorates covert operatives were employed in gathering information as to the destinations of the Shaper vessels. The seed fleets were allowed to leave, but would either find themselves ambused when they came out of SPEC to resupply (the key point being that, absent fuel, they would no longer be threats to meaningfully flee the ambush), or, for the sublight drifter fleets, chased down and exterminated. What few Shapers slipped through the Protectorates net would no longer constitute a people, a culture, or anything other than stray scattered individuals, living out the rest of their lives in exile. Historians would say of the war that, despite the Shapers superior intellects, which had led them on what should have been more successful strategies, it was the superior Andolian knowledge of the situation at hand that determined the outcome of the war. A combination of ignorance and mild hubris (belief, not that just that they could win, but that they deserved to, for being better than their Andolian competitors) proved fatal for the Shapers.

However, before their demise played out, the Shapers did leave a few more marks. The punitive plague-raid on the Uln (a simple killing virus) was far superior in efficacy to that on the Shmrn, and the Uln would prove notably cowed by the experience in their later negotiations with the First Empire. Realizing that the bio-weapon used by the Protectorate was of Rlaan origin, the Shapers incorrectly concluded that the Rlaan had collaborated with the Protectorate in engineering the Shaper demise, and likewise sent the Rlaan a farewell present targeting their civilian population  less perhaps a parting shot than a warning that the Rlaan would not be immune from the Shapers intended return. However, even in their shattered state, the Rlaan were adept at producing counter-viral agents, and the plague bombing was perceived more as an incomprehensible act of deranged malice than an action of war. This act by the Shapers was to prove fundamental to supporting the Protectorate arguments to the Rlaan, utterly aghast, nauseated, and made profoundly uneasy by the Protectorate tactics of the Culling fleet, that the Shapers were so deranged as to leave euthanizing them as the only option. Indeed, this act was so fundamental to the Protectorate arguments that there is much speculation as to whether Protectorate operatives may have played a role in convincing the Shapers to attack the Rlaan.

The Shapers sufficiently defeated, the Protectorate turned now to salvaging, rather than slaughtering the human survivors of the post-human war. Quarantine centers were organized on marginal, devastated worlds long abandoned by the Forsaken during the events of the Aeran war. There were so few survivors, that the operation, even given the ravaged nature of the Protectorate fleet and economy, was feasible. Actual Shaper worlds, rather than briefly conquered worlds, were not landed on for centuries, instead being dusted with radioactive materials, bombarded with asteroids and anti-matter bombs, seeded with counter-terraforming machines, and kept under constant vigilance and quarantine until no signs of life were visible. They would remain under quarantine even after this point until ground crews, only now visiting the planets, could verify no residual gifts lingering on. Where intransigent Shaper bio-forms were still found, they were rooted out until the planets were deemed sanitized, sterilized, and untainted, only then becoming eligible for re-terraforming. Rlaan, specifically Rlaan-Briin, were brought in to help clean up the bio-weapon mess that was the former human inhabited region of space. Compensation for this assistance, along with the new political and military realities, was to make the Rlaan-Briin, as an anthrophilic force within the Rlaan, the dominant group in Rlaan politics.

On a sad aside, the Dgn died along with their masters. Indeed, the only Dgn to survive the war would be those Dgn babies inflicted upon the Shmrn by the Shaper terror attack.

While many former human worlds were deemed too dangerous for human habitation, they were a fine environment for a new generation of Grandchildren to settle, for the first time moving out of their Andolian cradle. Backed by these new colonies of Grandchildren, the Protectorate would eventually become a different entity  the First Empire, expanding to include Shmrn, Uln, and eventually Rlaan space under a single sovereignty. This expansion would be one of implied, rather than exercised force, and would be performed through a series of peacefully negotiated annexations. 

Under the Empire, there would be a distinct split between those populations merging into the increasingly collective population of Andolian origin and those relegating themselves to an increasingly zoo-like status, preserved as the Ur-Human, Ur-Aeran, Ur-Rlaan, etc. on worlds both garrisoned under and protected by Grandchildren. The Grandchildren themselves would change as well, the garrison forces becoming increasingly detached from the path of the Empire, while the Grandchildren who became settlers of the former human worlds would become vital participants in all aspects of the Empire. As millennia passed, these divisions would come to have names, the Legion, the Ur-, the Firstborn, and the Inheritors, respectively. There also arose another class, beings constructed to bridge generational gaps within the Legion, who, due to their indefinite lifespans, were known as Methusalans. Though a very small portion of the total population, their role in monitoring and mitigating the negative effects of cultural drift would give them important positions within the Empire.

The Pax Legion would last for many generations before interruption by ex-Saahasayaay forces that had regrouped outside the jump network for some millennia. While the war was brutal, it was decisively won with knowledge gleamed from study of Ancient library information. However, evidence mounted that the aggression between the two sides both using vaguely Ancient derived technology had served to further rouse TWHON enitities. The majority of the Legions would end up heading off in a mass exodus to dwell around the deep-space devices responsible for maintaining the jump-network, as these would provide cover for further investigations into Ancient derived technology and limit the danger to the Ur. The Inheritors would remain behind to pursue their own ends absent the Legions supervision, with maintenance of contact and mitigation of drift falling to the Methusalas as the go-betweens.

This arrangement would last only for a few centuries before, in a series of tragic confusions, the return of the descendants of the 10,000 would once more break the peace.


